setpartitions_hyper2

### 2022-07-30 inst/setpartitions_hyper2.Rmd
multiset() not setparts()

```{r}
M <- apply(setparts(c(2,2,1)),2,function(x){letters[x]})
M
```

```{r}
f <- function(strength,help,vec){loglik(strength,cheering3(v=vec[1:4],e=c(a=1,b=2,c=3),help=help,vec[5]))}
help <- c(1.11,2.222,1.7345)
strength <- 1
```

>>>>

```{r}
M <- apply(multiset(c(1,1,2,2,3)),2,function(x){letters[x]})
noquote(M)
```

```{r}
tfun <- function(help,strength){
   out <- 0
     for(i in seq_len(ncol(M))){
     vec <- M[,i]
     out <- out +
       loglik(strength,cheering3(v=vec,e=c(a=1,b=2,c=3),help=help),log=FALSE)
   }
   return(out)
}

h <- c(1.11,2.222,1.7345)
print(tfun(help=(1:3)/10, strength= c(a=0.1,b=0.3,c=0.6)))
print(tfun(help=(7:5)/22, strength= c(a=0.3,b=0.2,c=0.5)))

```
